PyTracer: Automatically Profiling Numerical Instabilities in Python

### 2022-10-27 IEEEtran/paper.tex
Fit on 12pages

\pytracer's tracing overhead consists of (1) module instrumentation time
(initialization overhead) and (2) data write time during the execution (runtime
overhead). The initialization overhead is proportional to the number of
functions and classes traced. For example, we measured an average initialization
time of 8 seconds during our experiments with  NumPy, SciPy, and Scikit-learn.
This overhead can be reduced by excluding intensively used functions such as
\texttt{numpy.array} from the instrumentation.
Figure~\ref{fig:performance_tracing} summarizes \pytracer's tracing overhead for
SciPy and scikit-learn examples. \textit{Instrumentation and initialization} represents the slowdown of
\pytracer without fuzzy, \add{measured by applying PyTracer to Python programs without Monte-Carlo Arithmetic.}
The slowdown is measured as the ratio between the actual execution time
(without \pytracer) and the execution time using \pytracer. 
The \textit{Total with RR MCA} shows the slowdown within the Fuzzy environment.
Without Fuzzy, \pytracer introduces an average slowdown of $17\times$ for
the examples running less than 8 seconds because \pytracer spends most of its
time in the initialization step. Since this step is a constant factor of the
number of functions instrumented, we also measured the instrumentation cost
itself (\textit{Instrumentation only}) calculated by subtracting the
initialization time to \textit{Instrumentation}. We then obtain an average slowdown of
$3.5\times$. Finally, using MCA
operations (through Fuzzy) instead of the native ones increased the average
slowdown to $37\times$.
\add{As shown in Figure~\ref{fig:performance_parsing}, the log aggregation time is linearly correlated with the log trace size (F-score=68, p-value $\leq 10^{-8}$, obtained with the F-test for linear regression).}

>>>>

\pytracer's tracing overhead consists of (1) module instrumentation time
(initialization overhead) and (2) data write time during the execution (runtime
overhead). The initialization overhead is proportional to the number of
functions and classes traced. For example, we measured an average initialization
time of 8 seconds during our experiments with  NumPy, SciPy, and Scikit-learn.
This overhead can be reduced by excluding intensively used functions such as
\texttt{numpy.array} from the instrumentation.
Figure~\ref{fig:performance_tracing} summarizes \pytracer's tracing overhead for
SciPy and scikit-learn examples. \textit{Instrumentation and initialization} represents the slowdown of
\pytracer without fuzzy, \add{measured by applying PyTracer to Python programs without Monte-Carlo Arithmetic.}
The slowdown is measured as the ratio between the actual execution time
(without \pytracer) and the execution time using \pytracer. 
The \textit{Total with RR MCA} shows the slowdown within the Fuzzy environment.
Without Fuzzy, \pytracer introduces an average slowdown of $17\times$ for
the examples running less than 8 seconds because \pytracer spends most of its
time in the initialization step. Since this step is a constant factor of the
number of functions instrumented, we also measured the instrumentation cost
itself (\textit{Instrumentation only}) calculated by subtracting the
initialization time to \textit{Instrumentation}. We then obtain an average slowdown of
$3.5\times$. Finally, using MCA
operations (through Fuzzy) instead of the native ones increased the average
slowdown to $37\times$.
\add{As shown in Figure~\ref{fig:performance_parsing}, the log aggregation time is linearly correlated with the log trace size (F-score=68, p-value $\leq 10^{-8}$, F-test for linear regression).}
